Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-12 paper/main.tex
restructure (and mess up) discussion

\todo[inline]{RSC is not mentioned in intro anymore but it shows up in group
results (mixed in individual subjects) and therefore could be discussed}

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of faces
\citep{kanwisher1997ffa} or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.
% What is the PPA?
A classic example of a functionally defined, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{ epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes, buildings or landmarks \citep{aguirre1998area, epstein2014neural, epstein1998ppa} compared to e.g. pictures of tools of faces.
% spatial layout hypothesis
[[According to the spatial layout hypothesis, the PPA is involved in processing
the surface geometry of a visual stimulus and possibly in identifying scenes
based on their spatial layout \citep{epstein2010reliable}.]]\todo{better delete}
% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

@@

\todo[inline]{I deleted sentences regarding competing ``contextual associations
    hypothesis'' (\citep{aminoff2006parahippocampal, aminoff2013role}) because
our events/regressors cannot touch that issue; might be interesting during
discussion of anterior/posterior PPA.}

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices & FOV
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.  Slices were oriented to include the ventral portions of frontal and
occipital cortex while minimizing intersection with the eyeballs. The field of
view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [Oh, S. et
al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]. Auxiliary scans
for slice alignment and motion- and distortion-correction were performed at the
beginning of the first fMRI recording session and also after the break at the
start of the recording for the second half of the movie.

@@

\todo[inline]{I consider tables of significant clusters for every contrast as
overkill. One contrast, the ``primary contrast'', is appropriate}

\todo[inline]{s. comments for overview of individually significant clusters}

% all AO contrasts
% 1 geo, groom > non-geo:               PPA (l/r); RSC (l/r)
% 2 geo, groom, se_new > non-geo:       PPA (l/r); RSC (l/r)
% 3 groom, se_new, se_old > non-geo:    PPA (l/r); RSC (l/r)
% 4 geo > all non-geo PPA               PPA (l/r); RSC (l/r)
% 5 groom > all non-geo PPA             PPA (l/r); RSC (l/r)
% 6 se_new > all non-geo PPA            PPA (l/r); RSC (l/r)
% 7 se_new, se_old > all non-geo PPA               RSC (l/r)
% 8 se_new > se_old                     nothing
% 9 vse_new > vpe_old                              RSC (r)
%10 vse_new, vpe_new > vse_old, vpe_old nothing
%11 vse_new > vse_old                   nothing
%12 vse_new > vse_old, vpe_old          nothing
%13 vse_new, vpe_new > vpe_old          nothing

% all AV contrasts
% 1 vse_new > vpe_old: big bilateral cluster in PPA but also RSC, visual c.
% 2 vse_new, vpe_new > vse_old, vpe_old:
% group results are more more confined here
% (but individual results were probably worse)
% 3 vse_new > vse_old: PPA (l/r)
% 4 vse_new > vse_old, vpe_old: PPA (l/r)
% 5 vse_new, vpe_new > vpe_old: PPA (l/r) but also visual c.
% 6 vno_cut > vse_new: nothing
% 7 vno_cut > vse_old: nothing
% 8 vno_cut > vse_new, vse_old: nothing
% 9 vno_cut > vpe_new, vpe_old: nothing
%10 se_new > se_old: right PPA

% why we did different contrasts
We created different $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and for the AV stimulus (see Table
\ref{tab:av-contrasts}) to test the stability of results across different
contrasts and exclude accidental findings.
% results
The overlap of significant clusters of the eight contrast for the
audio-description, and five contrasts computed for the movie can be found in
Figure \ref{fig:stability-slices}.
% results in PPA
Six of eight AO contrasts show significant bilateral clusters in anterior
regions of the group PPA overlap.\todo[inline]{temporal occipital fusiform gyrus
according to Harvard-Oxford Cortical Structural Atlas}
% Precuneus = retrosplenial cortex ?
Six of eight contrasts show significant clusters in the retrosplenial region
(and ventral precuneus).
% statement/answer
This suggest results are reproducible in a variety of contrasts and do not
depend on the design of one specific contrasts.
% individual results
Notably, we chose one contrast to look into individual results of all subjects
but individually a contrast different from the primary contrast might lead to
better individual localization results.

% AV intro
For the analysis of the AV stimulus, we created five contrasts for a cross-modal
comparison.
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% lingual gyrus
In three contrasts, these homologous clusters extend into the lingual gyri.
% RSC
Further, three contrasts show significant homologous clusters in the RSC.
% LOC
Lastly, four contrasts show significant homologous clusters in lateral occipital
cortices.
% statement/answer
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts.

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
        p<.05, cluster corrected) of contrasts created to isolate the PPA.
        Contrasts provide decreasing congruency with the spatial layout
        hypothesis and/or progressively less data/events. The overlap across
        contrasts is overlaid on the MNI152 T1-weighted head template (gray).
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}). Blue: contrasts 1-7 for the
        audio-description (see Table \ref{tab:ao-contrasts}. Red: contrasts 1-5
        for the audio-visual movie (see Table \ref{tab:av-contrasts}. Black:
        outline of overlapping individual PPA ROIs
        \citep{sengupta2016extension}.} \label{fig:stability-slices}
    \end{figure*}

@@

\todo[inline]{e.g. We demonstrate\dots; we discovered\dots; our data provide
evidence\dots}

% previous studies
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to face or
objects \citep{epstein1998ppa, epstein1999parahippocampal} whereas a study using
spoken sentences reported mixed results \citep{aziz2008modulation}.
% what we wanted to test
Hence, we tested if the perception of verbal spatial cues embedded in an
auditory narrative contrasted with non-spatial cues correlate with increased
activation in the PPA.
% ``how'' we did it
We use analogous statistical models in three different experimental paradigms to
compare results gained from a dedicated visual localizer to results we gained
from a movie and the movie's audio-description.

\todo[inline]{high-level summary/interpretation of results in one sentence here
already?}

@@

\todo[inline]{could maybe pasted into method section to save space here; a short
interpretation is already given there already}
% stimuli not designed for research purposes
Both naturalistic stimuli were not designed to be used in a BOLD fMRI experiment
but to entertain their audiences.
% why correlation matrix  was created
Thus, we first tested for correlation of regressors (s. \ref{fig:reg-corr}) that
are based on the annotated stimulus features because a high degree of shared
variance lowers detection power
% results of computing feature correlation
Results show no to minor correlations of regressors across all stimulus
segments.
% encouraged by that we build contrasts (statement)
Thus we felt encouraged to create traditional/canonical voxel-wise GLMs that
modeled and contrasted hemodynamic activity similarly to previous studies that
used simplified stimuli.

@@

\todo[inline]{discuss only PPA here}
% intro
We performed whole-brain analyses on a group level and individual level. In both
naturalistic stimuli, significantly increased activity in the PPA correlates
with spatial events compared to non-spatial events.

@@

\todo[inline]{Do Wilson (2008), Lerner (2011), Honey (2012), Silbert (2014) find
ISC in PPA using an auditory stimulus?}
% AO stimulus cluster location
More specifically for the primary contrast of the AO stimulus, group results
show spatially concise / restricted clusters in the anterior part of the PPA
group overlap taken from \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
model a hemodynamic response but modeled an event from on- to offset of each
word that was giving the cue about the movie's missing visual content of a
scene.
% conclusion
Our group results suggest that auditory spatial information does not just
modulate activity in the PPA (depending on other factors like familiarity; s.
\citep{aziz2008modulation}) but correlates with bilaterally increased
activation.\todo{``modulate'' suggests causation}

% no task in Epstein
An early block-design study \citep{epstein1998ppa} that compared results from a
paradigm that employed a (perceptual) judgment task of static pictures to a
paradigm without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Our paradigm still differs from previous studies because the relevant stimulus
features were incidentally embedded in a continuous auditory (or audio-visual)
stream.
% conclusion
This embeddedness prevents participants from making assumptions about the
investigated perceptual process by just being exposed to the paradigm and thus
mimics experiencing the world outside the lab more closely.
% concluding statement: kinda automatic process
The lack of a task further suggests verbal spatial information is processed in
the PPA in an automatic fashion and does not necessarily rely on deliberately
paying attention to spatial information.

\paragraph{shortcomings of AO contrasts}
% no ``landscape'' category
Our primary contrasts compared verbal cues regarding landmarks ((\texttt{geo};
often buildings or aspects of a whole scene) and elements defining the geometry
of a room (\texttt{groom}) to non-spatial cues.
% vs vision
In the visual domain, whole landscapes and not pictures of landmarks are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).
% our se_new & se_old
The audio-description's narrator rarely described a whole landscape by a single
word (e.g. ``in a football stadium'', ``Forrest is running through the jungle'')
when the plot switch from one setting to another setting but usually by
continuously adding more concrete spatial cues (e.g. landmarks like buildings,
trees, and streets)
% further studies
Humans can identify the gist of a rich visual scene within the duration of a
single fixation \citep{henderson2003human}. Hence, further studies might
investigate if vague verbal descriptions of a scene as a whole lead to
differential hemodynamic activity in the PPA compared to more concrete spatial
cues.

\subsubsection{AV stimulus}

% location
Clusters of the analysis of the AV stimulus span the group overlap of individual
PPAs from anterior to posterior and retrosplenial regions bilaterally.
% difference in location/size to AO and VIS
Clusters also extend into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex) \todo{s. neurosynth in fsleyes?}
% confound of higher perception
This can be attributed to the fact that we averaged the content of individual
frames after a cut and did not control for confounding features like depicted
faces or objects.
% confounds of lower perception
It further suggest low-level visual features were not averaged out leading to
clusters spanning the intracalcarine cortex.
% further studies
Hence, further studies focusing on visual perception should annotate and model
visual features of naturalistic stimuli more rigorously.

\subsubsection{stability of contrasts}

% why we did a couple of contrasts
For both stimuli we created additional contrasts that varied the amount of
events available for the analysis and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.
% it shows two thing
\todo[inline]{in how many clusters are how many overlapping clusters}
% no incidental findings
The results of the additional contrasts suggest that increased activation within
the PPA is not just an accidental finding.  The bilaterally increased activation
in the PPA does not depend on accidental findings but are stable across
contrasts.
% decline in isolation power
Nevertheless, the ability to isolate the PPA drops the less the amount of data
are available and the less the events averaged to built a category match the
preferred stimulus type processed in the PPA.
% decline b)
Second, the ability to isolate clusters in the PPA declines nevertheless
depending on the amount of events available to the statistical model. More
importantly, isolation ability also declines depending on how well the used
events within categories matched on average the preferred stimulus type. (cf.
\texttt{se\_new} and \text{se\_old} in contrast 6-8)
% concluding statement hypothesis
Moreover, nouns of the narrator cueing a switch to another setting are often
forestalled by changes of the soundscape.
% arnott
\todo[inline]{arnott2008crinkling find increased activations of PPA to sound
made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.

\todo[inline]{arnott2008 might be a good opportunity to switch to more general
assumption of ``contextual information'' and combine that switch with
anterior/posterior discussion}

\paragraph{bilateral superior lateral occipital cortex}

\paragraph{RSC}

% but RSC
Apart from the PPA, we find significantly increased activity consistently across
contrast in the retrosplenial cortex (RSC).\todo{how many exactly?}

@@

@@

\paragraph{(non-existing) other cluster}

\todo[inline]{AV stimulus: we DID NOT find clusters that could be attributed to
top-down / bottom-up attention, eye movements (FEF) (cf. corbetta2002control)
or memory (which memory)?}

% whole brain analysis
Regarding confounding variables, we do not find significant clusters in e.g.
early auditory cortices despite performing a whole brain analysis on data gained
from a naturalistic stimulus paradigm.
% conclusion
This suggests that variance correlating with lower level auditory processes was
averaged (out) across trials and/or regressed out by implementing the nuisance
regressors.
% shit was averaged out we did not even know of
Further, unknown stimulus features we did not even annotate did not lead to a
variety of significant cluster across the brain that hamper interpretation of
results.
% conclusion
This provides further evidence that model-driven analyses can be run on data
from naturalistic stimuli to isolate brain activity correlating with specific
perceptual processes.

@@

\todo[inline]{could be mentioned in a few sentences. But above topics a far too
much still}

>>>>

\todo[inline]{retrosplenial cortex is not mentioned in intro anymore but it
shows up in group results (mixed in individual subjects) and therefore should
be discussed}

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of faces
\citep{kanwisher1997ffa} or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.\todo{kinda aggressive introductory
sentence}.
% What is the PPA?
A classic example of a functionally defined, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes, buildings or landmarks \citep{aguirre1998area,
epstein2014neural, epstein1998ppa} compared to e.g. pictures of tools of faces.
% spatial layout hypothesis
[[According to the spatial layout hypothesis, the PPA is involved in processing
the surface geometry of a visual stimulus and possibly in identifying scenes
based on their spatial layout \citep{epstein2010reliable}.]]\todo{better delete}
% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

@@

\todo[inline]{``contextual associations hypothesis''
(\citep{aminoff2006parahippocampal, aminoff2013role}) does not show up in intro
anymore; events/regressors cannot touch that issue; might be interesting during
discussion of anterior/posterior PPA.}

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices & FOV
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.  Slices were oriented to include the ventral portions of frontal and
occipital cortex while minimizing intersection with the eyeballs. The field of
view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [Oh, S. et
al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011]. Auxiliary scans
for slice alignment and motion- and distortion-correction were performed at the
beginning of the first fMRI recording session and also after the break at the
start of the recording for the second half of the movie.\todo{references to bib}

@@

\todo[inline]{I consider tables of significant clusters for every contrast as
overkill. Tables for just the ``primary contrast'', seems more appropriate}

\todo[inline]{s. comments for overview of sign. clusters in all contrasts}

% why we did different contrasts
We created different $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and for the AV stimulus (see Table
\ref{tab:av-contrasts}) to test the stability of results across different
contrasts and exclude accidental findings.

% all AO contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r)
% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
% 4 PPA (l/r); RSC (l/r), LOC (l/r)
% 5 PPA (l/r); RSC (l/r), LOC (-/-)
% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
% 8 PPA (-/-); RSC (-/-), LOC (-/-)
% control contrasts
% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
%10 PPA (-/-); RSC (-/-), LOC (-/-)
%11 PPA (-/-); RSC (-/-), LOC (-/-),
%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
%13 PPA (-/-); RSC (-/-), LOC (-/-)

% results
The overlap of significant clusters of the eight contrast for the
audio-description, and five contrasts computed for the movie can be found in
Figure \ref{fig:stability-slices}.
% results in PPA
In the analysis of the AO stimulus, six of eight contrasts show significant
bilateral clusters in anterior regions of the group PPA
overlap.\todo[inline]{temporal occipital fusiform gyrus according to
Harvard-Oxford Cortical Structural Atlas}
% Precuneus = retrosplenial cortex ?
Seven of eight contrasts show bilaterally significant clusters in the
retrosplenial region (and ventral precuneus).
% statement/answer
This suggest results are reproducible in a variety of contrasts and do not
depend on the design of one specific contrasts.
% individual results
Notably, we chose one contrast to look into individual results of all subjects
but individually a contrast different from the primary contrast might lead to
better individual localization results.
% transverse occipital sulcus
\todo[inline]{transverse occipital sulcus / occipital place area? in 6 of 8
contrasts}
% confounds
but confounds: right superior temporal gyrus (4 contrasts); left superior
temporal gyrus (3 contrasts); some prefrontal clusters that show up in two
contrasts
% control in AO contrasts
\todo[inline]{control contrast essentially almost all none results; s. comments}

% all AV contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r), intracalcarine, cuneal, ling.c
% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
% control contrasts
% 6 nothing
% 7 nothing
% 8 nothing
% 9 nothing
%10 se_new > se_old (nouns in AV stim): LOC (l/r)
% right PPA, bilateral sup. lat. occ. c., superior parietal lobe (right)

% AV intro
For the analysis of the AV stimulus, we created five contrasts for a cross-modal
comparison.
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% lingual gyrus
In three contrasts, these homologous clusters extend into the lingual gyri.
% RSC
Further, three contrasts show significant homologous clusters in the RSC.
% LOC
Lastly, four contrasts show significant homologous clusters in lateral occipital
cortices.
% statement/answer
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts.
% control AV
\todo[inline]{control in AV stim: se\_new > se\_old (nouns in AV stim): LOC
(l/r), right PPA, bilateral sup. lat. occ. c., superior parietal lobe (right)}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Stability of contrasts. Overlap of significant clusters (Z>3.4;
        p<.05, cluster corrected) of contrasts created to isolate the PPA.
        Contrasts provide decreasing congruency with the spatial layout
        hypothesis and/or progressively less data/events. The overlap across
        contrasts is overlaid on the MNI152 T1-weighted head template (gray).
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}). Blue: contrasts 1-8 for the
        audio-description (see Table \ref{tab:ao-contrasts}. Red: contrasts 1-5
        for the audio-visual movie (see Table \ref{tab:av-contrasts}. Black:
        outline of overlapping individual PPA ROIs
        \citep{sengupta2016extension}.} \label{fig:stability-slices}
    \end{figure*}

@@

% previous studies: visual
On the one hand, previous studies reported bilaterally increased hemodynamic
activity in the PPA when participants were watching static pictures of landscape
compared to face or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal})
% previous study: auditory
On the other hand, a study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% what we did
Hence, we use analogous statistical models in three different experimental
paradigms to compare results gained from a dedicated visual localizer to results
we gained from a movie and the movie's audio-description.
% We focus
Our results suggest that the perception of verbal spatial cues embedded in an
auditory narrative contrasted with non-spatial cues correlate with increased
activation in the PPA of both hemispheres.

@@

\todo[inline]{could maybe pasted into method section to save space here; a short
interpretation is given there already}
% stimuli not designed for research purposes
Both naturalistic stimuli were not designed to be used in a BOLD fMRI experiment
but to entertain their audiences.
% why correlation matrix  was created
Thus, we first tested for correlation of regressors (s. \ref{fig:reg-corr}) that
are based on the annotated stimulus features because a high degree of shared
variance lowers detection power
% results of computing feature correlation
Results show no to minor correlations of regressors across all stimulus
segments.
% encouraged by that we build contrasts (statement)
Thus we felt encouraged to create traditional/canonical voxel-wise GLMs that
modeled and contrasted hemodynamic activity similarly to previous studies that
used simplified stimuli.

@@

\todo[inline]{discuss only PPA here}
% intro
We performed whole-brain analyses on data from the audio-visual movie and its
audio-description. We chose one contrast of each stimulus to be investigated not
just on a group level but also on the level of individual subjects. Additional
contrasts were tested to investigate the stability of results across contrasts
when contrasted categories and the amount of available data is varied.

@@

% AO stimulus cluster location
Group results of the AO stimulus' primary contrast yielded spatially
concise / restricted clusters in the anterior part of the PPA group overlap
taken from \citep{sengupta2016extension}.
% diff to Aziz (2008)
Unlike \citep{aziz2008modulation} we did not use whole sentences as events to
model a hemodynamic responses but modeled from on- to offset of single words
that cue the listener about the movie's missing visual content.
% conclusion
Our group results suggest that auditory spatial information does not just
modulate activity in the PPA (depending on other factors like familiarity; s.
\citep{aziz2008modulation}) but correlates with bilaterally increased
activation.\todo{``modulate'' suggests causation}

% no task in Epstein
An early block-design study \citep{epstein1998ppa} compared results from a
paradigm that employed a (perceptual) judgment task of static pictures to a to
the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Nevertheless, our paradigm still differs from previous studies because the
relevant stimulus features were incidentally embedded in a continuous auditory
stream.
% conclusion
This embeddedness prevents participants from making assumptions about the
investigated perceptual process by just being exposed to the paradigm and thus
mimics experiencing the world outside the lab more closely.
% concluding statement: kinda automatic process
The lack of a task further suggests verbal spatial information is processed in
the PPA in an automatic fashion and does not necessarily rely on deliberately
paying attention to spatial information.

\paragraph{shortcomings of AO contrasts}
% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% cateogries in primary contrasts
In the current study's primary contrast, we compared verbal cues regarding
landmarks ((\texttt{geo}; often buildings or other single aspects of a whole
scene) and elements defining the geometry of a room/locale (\texttt{groom}) to
non-spatial cues.
% we did not choose se\_new and se\_old
Notably, we did not choose the categories that contained switches from one
setting to another (texttt{se\_new} and texttt{se\_old}) which one might assume
to contain the auditory equivalent to the ``optimal'' visual stimulus type.
% why not se\_new or se\_old
These categories were actually heterogeneous: they rarely contained whole (but
also vague) descriptions of landscapes (e.g. ``in a football stadium'',
``Forrest is running through the jungle''), mostly landmarks or buildings,
and they also contained non-spatial cues.\todo{repeat examples from method
section}.
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if categories of vague verbal descriptions of a landscape as a whole
lead to differential hemodynamic activity in the PPA compared to more concrete
spatial cues.

\subsubsection{AV stimulus}
% location
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPAs from anterior to posterior and
expand into retrosplenial regions.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex) \todo{what overlaps with group ROI?}
% confound of higher perception
This can be attributed to the fact that we averaged the content of individual
frames after a cut and did not control for confounding features like depicted
faces or objects.
% confounds of lower perception
It further suggest low-level visual features were not averaged out leading to
clusters spanning the intracalcarine cortex.
% further studies
Hence, further studies focusing on visual perception should annotate and model
visual features of naturalistic stimuli more rigorously.
\todo[inline]{concluding statement to cross-modality of results?}

\subsection{stability of contrasts}

% why we did a couple of contrasts
For both stimuli we created additional contrasts that varied the amount of
events available for the analysis and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.

\subsubsection{PPA}
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show
significant bilateral clusters in the anterior part of the group PPA.
% PPA AV
Regarding contrasts of the AV stimulus, x of y contrasts show significant
bilateral clusters in the PPA but extending into posterior regions
% no incidental findings
Results of the additional contrasts suggest that bilaterally increased
activation in the PPA does not depend on accidental findings but is are stable
across contrasts of the movie and the audio-description.
% anterior vs. posterior?

\subsubsection{localization performance and noise}
% overall good isolation;  whole brain analysis and not many random clusters
Despite performing a whole brain analysis on naturalistic stimuli with many
uncontrolled stimuli we do not find many random clusters in single contrasts or
even systematically across contrasts\todo{good god but that's essentially it}.
% shit was averaged out we did not even know of
Further, unknown stimulus features we did not even annotate did not lead to a
variety of significant cluster across the brain that hamper interpretation of
results.
% movie: attention, and shit
\todo[inline]{where are no clusters? e.g. top-down / bottom-up
attention, eye movements (FEF) (cf. corbetta2002control) or memory (which
memory)?}

% BUT: amount of data
Nevertheless, localization performance depends on the amount of available
data\todo{give examples of contrast using less events in AV and AO}.
% BUT: match of the stimulus type/averaged events
Further, localization performance is also influenced by how well events
within categories matched on average the preferred stimulus type.
% AV: frame content
In the AV stimulus, we averaged different kind of movie cuts regardless to the
movie frames content.
\todo[inline]{how well spatially constrained are the clusters?}
% AO: stimulus categories
Moreover, nouns of the narrator cueing a switch to another setting are often
forestalled by changes of the soundscape.\todo{cross-modal control contrasts;
all negative results at moment of cuts but vse\_new > pe\_old): right RSC.}
% arnott
\todo[inline]{e.g. arnott2008crinkling find increased activations of PPA to
sound made by objects}
% hypothesis
We hypothesize that not just semantic information but also the mere changes of a
soundscape that cues a listener about a setting's spatial layout of could
correlate with increased activity in the PPA.
% AO: superior temporal cortex
Nevertheless in four of nine contrasts of the AO stimulus, we find significant
clusters in superior auditory cortices (including early auditory
cortices?)\todo{which exactly}
% conclusion
This suggests that variance correlating with lower level auditory processes was
(not) averaged (out) across trials\todo{which contrasts; A1 \& low-level
nuisance regressors?}

% conclusion: AO and AV stability
In summary, our results across add further evidence that model-driven analyses
can be run on data from naturalistic stimuli to isolate brain activity
correlating with specific perceptual processes.
% but
Nevertheless isolation performance relies on how well the model captures
different aspects of the stimuli's feature space.

\subsubsection{other systematics: anterior vs. posterior, RSC and OPA}

% intro
Nevertheless, results across contrasts of both stimuli show significant clusters
constrained to the anterior part of the PPA in contrasts of the AO stimulus, and
significant clusters in the retrosplenial cortices and superior lateral cortices
in both naturalistic stimuli.

@@

\todo[inline]{at the moment it makes more sense to discuss it sooner; but it
kinda depends on stuff that is happening in the RSA too}

@@

\paragraph{RSC (in both stimuli)}

% but RSC
Apart from the PPA, we find significantly increased activity consistently across
contrast of both contrasts in the retrosplenial cortex (RSC).\todo{how many
exactly?}

\paragraph{superior lateral occipital cortex (in both stimuli)}

\todo[inline]{could be mentioned in a few sentences. But above topics a far too
much still; better embed somewhere above}

@@
